Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-22 Latex/journal_v1/V5/pr.tex

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G i.e eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\end{itemize}

@@

The other parameters of these simulations are depicted in Table \ref{table:1a}.
\begin{table}
 \caption {Simulation Parameter} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Parameter & Value \\ [0.5ex]
  \hline\hline
  Noise power & -174dBm\\
  \hline
  Bandwidth & 180 KHz \\
  \hline
 Maximum transmit Power of each O-RU & 40dBm \\
  \hline
  Maximum delay for eMBB &  4msec \\
  \hline
    Maximum delay for URLLC &  1msec \\
  \hline
  Maximum delay for mMTC &  5msec \\
  \hline
  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
   \hline
  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
  \hline
   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
  \hline
   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
  \hline
    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
  \hline
 \end{tabular}
 \end{center}
 \end{table}

@@

The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
\subsection{Feasible Region}\label{fr}
Applying the correct initial point to make the system feasible is a significant step in our work.
During the simulation, it can be noted that sometimes the algorithm does not converge in a number of these simulations for a certain number of UEs.
For a fixed number of UEs, by comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, UEs are at the edge of the boundaries or far away from the O-RU and have a weak channel gain. One solution is to eliminate UEs who undermine system convergence.
Another solution is to remove the simulations in the mont-Carlo that do not converge.
To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
the proposed algorithm (IABV). 
If the conditions \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
The FA algorithm is depicted as algorithm \ref{alg3}.
 \begin{algorithm}
\caption{Fast Algorithm to Check the Convergence (FA)}\label{alg3}
\begin{algorithmic}[1]
\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
\State Assume the number of PRBs is $K$
\State Assume $d_{r,u(s,i)}$ is the distance from the $r^{th}$ O-RU to the UE i in slice s
\State Set count = 0 
\State Set $p_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $e_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $g_{u(s,i)}^{r} = 0 \quad \forall r,s,i$
\For{$s \gets 1$ to $S$} 
\For{$i \gets 1$ to $U_s$}
\State count = count +1  
\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
\State $g_{u(s,i)} ^{r^*}=1$
\State temp =mod(count, K)            
\If {temp=0 }
\State $e_{r^*,u(s,i)}^{K} = 1 $
\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
\Else 
\State $e_{r^*,u(s,i)}^{temp} = 1 \quad \forall r$ 
\State Set $p_{r^*,u(s,i)}^{temp} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
\EndIf

\State \textbf{end if}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
In the algorithm FA, the O-RU association is based on the distance of the UE to the O-RU. 
Each UE is associated with the nearest O-RU. Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{max}, P_r^{max}/\mathfrak{N}\}$).
Moreover, the allocation of physical resources to users is based on dividing the UE number by the total number of PRBs.
If the number of UE is more than the resources, each UE is given exactly one PRB without interference, otherwise the amount of interference will be very low.
\subsection{Numerical Results}
In Fig. \ref{fig:1} the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods. Suppose we have one service instance for each type of service, so we have three various services in this figure. Also We have between 6 and 48 UEs in the system.
Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increases. Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{Arate_ue1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
  \label{fig:1}
\end{figure}
%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
%  \label{fig:3}
%\end{figure}

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power. 
Assume each UE in each mMTC service instance requires 1bits/sec/Hz data rate and is not sensitive to the end-to-end delay. Also, suppose the fronthaul link has no restrictions. The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. 
Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.4]{AmmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UEs in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}

>>>>

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G i.e eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}

@@

Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.

The other parameters of these simulations are depicted in Table \ref{table:1a}.
\begin{table}
 \caption {Simulation Parameter} \label{table:1a}
 \begin{center}
  \begin{tabular}{||c c ||}
  \hline
Parameter & Value \\ [0.5ex]
  \hline\hline
  Noise power & -174dBm\\
  \hline
  Bandwidth & 180 KHz \\
  \hline
 Maximum transmit Power of each O-RU & 40dBm \\
  \hline
  Maximum delay for eMBB &  4msec \\
  \hline
    Maximum delay for URLLC &  1msec \\
  \hline
  Maximum delay for mMTC &  5msec \\
  \hline
  Maximum fronthaul capacity  & 46 bits/sec/Hz \\
   \hline
  Minimum data rate for eMBB &  20 bits/sec/Hz \\ 
  \hline
   Minimum data rate for URLLC and mMTC &  2 bits/sec/Hz \\ 
  \hline
   Maximum received power for mMTC &  20 dBm \\ [.5ex]   
  \hline
    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   
  \hline
 \end{tabular}
 \end{center}
 \end{table}

@@

The second one is similar to the FBDR algorithm proposed in \cite{lee2018dynamic}. In this method, PRB and power are dynamically allocated, and the number of VNFs is obtained from the simulation, and the UEs are associated with the O-RU based on the quality of their channels and the channel distance.
\subsection{Feasible Region}\label{fr}
Applying the correct initial point to make the system feasible is a significant step in our work.
During the simulation, it can be noted that sometimes the algorithm does not converge for some of the iterations with fixed initial values.
To solve this problem, we investigated the non-converging and converging simulation for models with fixed initial parameters (such as number of UEs, the threshold of power and rate,... ) and random channel gains of UEs.
By comparing convergent and non-convergent simulations, we experimentally found that in cases where convergence does not occur, there are UEs at the edge of the boundaries or far away from the O-RU and have a weak channel gain. One solution is to eliminate UEs who undermine system convergence.
For a large number of UEs with a fixed number of PRBs, the probability of having an infeasible solution increases due to a large number of UE interferences.
Another solution is to remove the simulations in the mont-Carlo that do not converge.
In the simulation part, if more than half of the iterations have a feasible solution for the initial condition, the simulation can be displayed as a feasible model.
To remove non-converging simulations, we need to use a fast algorithm (FA) to check the convergence before
the proposed algorithm (IABV). 
If the conditions \eqref{RConstr}, \eqref{pr11}, \eqref{c12-1} and \eqref{c12} are met in the fast algorithm (FA), the given algorithm will converge.
The FA algorithm is depicted as algorithm \ref{alg3}.
 \begin{algorithm}
\caption{Fast Algorithm to Check the Convergence (FA)}\label{alg3}
\begin{algorithmic}[1]
\State Assume the number of UEs is $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_s}1$
\State Assume the number of PRBs is $K$
\State Assume $d_{r,u(s,i)}$ is the distance from the $r^{th}$ O-RU to the UE i in slice s
\State Set count = 0 
\State Set $p_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $e_{r,u(s,i)}^{k} = 0 \quad \forall r,k,s,i$
\State Set $g_{u(s,i)}^{r} = 0 \quad \forall r,s,i$
\For{$s \gets 1$ to $S$} 
\For{$i \gets 1$ to $U_s$}
\State count = count +1  
\State $r^* = \argmin_r d_{r,u(s,i)} \quad \forall r$
\State $g_{u(s,i)} ^{r^*}=1$
\State temp =mod(count, K)            
\If {temp=0 }
\State $e_{r^*,u(s,i)}^{K} = 1 $
\State Set $p_{r^*,u(s,i)}^{K} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
\Else 
\State $e_{r^*,u(s,i)}^{temp} = 1 \quad \forall r$ 
\State Set $p_{r^*,u(s,i)}^{temp} = \min\{P_s^{max}, P_r^{max}/\mathfrak{N}\} $
\EndIf

\State \textbf{end if}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
The complexity order of this algorithm is $O(R\times \mathfrak{N})$ which is remarkably lower than the complexity order of the IABV method.
In the algorithm FA, the O-RU association is based on the distance of the UE to the O-RU. 
Each UE is associated with the nearest O-RU. Also, the power of each UE is set to be the minimum of the maximum power of each UE and the maximum power of each O-RU divided by the total number of UEs ($\min\{P_s^{max}, P_r^{max}/\mathfrak{N}\}$).
Moreover, the allocation of PRBs to UEs is based on dividing the UE number by the total number of PRBs.
If the number of UE is more than the PRBs, each UE is given exactly one PRB without interference. Otherwise, the amount of interference will not be high but more than one UE will use same PRBs.
\subsection{Numerical Results}
In Fig. \ref{fig:1} the aggregate throughput is demonstrated versus the different number of UEs in each service for these three methods. Suppose we have one service instance for each type of service, so we have three various services in this figure. Also We have between 6 and 48 UEs in the system.
Here, we did not consider the priority. The figure presented that the proposed method (IABV) is $18.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increases. Still, due to the interference and the power constraint, it will be saturated from 12 UEs in each service.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{Arate_ue1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in each Service In the Presence of Three Services}
  \label{fig:1}
\end{figure}
%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
%  \label{fig:3}
%\end{figure}

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power. 
Assume each UE in each mMTC service instance requires 0.5 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. Also, suppose the fronthaul link and the number of VNFs have no restrictions.
Moreover, to make the simulation feasible, we assume that the number of PRBs is as large as the system has no interference, so we suppose there is a fixed  PRB allocation in the simulation that each UE is allocated to one PRB. There is no PRB with more than one UE allocation.
The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. 
Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.4]{AmmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UEs in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}
